### 2012-04-06 mindreading/minimal theory of mind (new version)/minimal theory of mind.nv.tex
mtom redraft got to end

@@

To make the question more precise it is useful to distinguish 
theory of mind abilities from theory of mind cognition.  
A  \textit{theory of mind ability} is an ability that exists in part because exercising it brings benefits obtaining which depends on exploiting or influencing facts about others’ mental states.
To illustrate,
suppose that Hannah is able to discern whether another's eyes are in view,
that Hannah exercises this ability to escape detection while stealing from others,
that Hannah's ability exists in part because it benefits her in this way,
and 
that Hannah's escaping detection depends on exploiting a fact about other's mental states (namely that they usually cannot  see Hannah's acts of theft when Hannah doesn't have their eyes in view).
Then Hannah has a theory of mind ability.
(This is not supposed to be a plausible, real-world example but only to illustrate what the definition requires.)
An ability to \textit{track} perceptions or beliefs (say) is a theory of mind ability which involves exploiting or influencing facts about these states.
By contrast, \textit{theory of mind cognition} involves representing mental states or processes as such.
And \textit{full-blown} theory of mind cognition involves  representing propositional attitudes such as beliefs, desires and intentions to construct reason-giving, causal explanations of action.  
The distinction between theory of mind abilities and theory of mind cognition matters because the facts about other minds which theory of mind abilities exploit are not necessarily the facts which are represented in theory of mind cognition.  
To return to the illustration, Hannah is able, within limits, to exploit facts about what others perceive without representing perceptions as such. 
She has a theory of mind ability while possibly lacking any theory of mind cognition.

@@

The notion that some abilities to track perceptions or beliefs involve only on theory of mind cognition which does not involve representing perceptions or beliefs as such is not entirely novel.
To mention only those we draw most directly on, Gomez (\citeyear[][p.\ 730]{en_1259}) has emphasized primitive intentional relations to objects established by gaze, O’Neil and Doherty have separately discussed a notion of engagement with objects (\citealp{en_1159, en_1140}), Call and Tomasello (\citeyear[][p.\ 58]{en_1669}) have suggested that chimpanzees track the `likely target' of others’ visual access and understand something about its effects on behaviour, and Whiten (\citeyear[]{en_1415, en_1416}) uses the notion of an `intervening variable' to explain primitive theory of mind notions.  These are illuminating ideas and what follows can be seen as an elaboration and partial synthesis of them.  
The result---minimal theory of mind---is unlike its precursors in that it is rich enough to explain systematic success on a range of false belief tasks.  Our approach is novel in this and others respects to which we return (in the Conclusion) after presenting the substance of our account.

@@

\section{Motivation}
Our question is theoretical: it concerns 
not what anyone does represent
but what someone could represent that would enable her, at least within limits, to track perceptions, knowledge states and beliefs.
The motivation for facing up to this question is, of course, partly empirical.

@@

\section{More motivation}
Further motivation for our question comes from evidence for theory of mind abilities in young children and infants.
Children in their second year use pointing to provide information to others \citep[]{en_1093} in ways that reflect a partner’s ignorance or knowledge \citep[]{en_1699}, as well as providing more information to ignorant than knowledgeable partners when making requests \citep[]{en_1140}.  One-year-old children also predict actions of agents with false beliefs about the locations of objects \citep[]{en_1092, en_1208} and choose different ways of interacting with others depending on whether their beliefs are true or false \citep[]{en_1783,Knudsen:2011fk,southgate:2010fb}.  And in much the way that irrelevant facts about the contents of others’ beliefs modulate adult subjects’ response times, such facts also affect how long 7-month-old infants look at some stimuli \citep[]{kovacs_social_2010}.

@@

Theory of mind abilities are not only found in humans.
For instance,
scrub-jays can selectively re-cache their food in ways that deprive competitors of knowledge of its location \citep{Clayton:2007fh}, and  chimpanzees can both select routes to approach food which conceal them from a competitor’s view \citep[]{en_1546} and also retrieve food using strategies that optimize their return given what a dominant competitor has seen \citep[]{en_1545}.  
There is debate about the cognitive underpinnings of these abilities (e.g.\ 
	\citealp{povinelli:2004vonk, 
			Penn:2007ey,
			Tomasello:2005ce,
			Call:2008di}). 
If it is not yet known precisely what explains these abilities 
and if the available evidence does not already tightly constrain the space of admissible conjectures,
then the construction of a minimal theory of mind may be relevant to these debates.
For the conjecture that minimal theory of mind explains chimpanzees' or scrub-jays' abilities to track perceptions or beliefs can be empirically distinguished from conjectures about representations of nonintentional behaviour only and from conjectures about representations of perceptions, knowledge states and beliefs (as we explain in section *** below).

@@

\section{The need for a constructive approach}
Davidson ...

%This is reflected in the dichotomy between behaviour reading (P&Vonk) \& full-blown ToM (Baillargeon review).

Davidson might be right about ordinary, commonsense psychology.

So a constructive approach is needed. ***

@@

The second principle has many applications.  Someone who is aware of this principle can be motivated to prevent others from encountering her food even when they are not in a position to steal it immediately.  Take scrub-jays.  When choosing where to cache food in the presence of a competitor they prefer far to near, darker to lighter, and occluded to in-view locations \citep[]{en_1451, en_1452}.  These scrub-jays may be trying to hinder future thefts, for these behaviours are not found when caching non-food items \citep[]{en_1419} or when caching in the presence of a partner \citep[][p.\ 514]{en_1418, en_1408}.  Clayton and Emery note that `[s]uch skills suggest visual perspective taking—computing what another can or cannot see' \citep[]{en_1451}. That is to say, they ascribed to scrub jays the concept of seeing.  Another possibility is that scrub-jays compute encountering rather than seeing.  Perhaps scrub-jays take having encountered food to be a condition for performing goal-directed actions targeting that food.  If so they may be trying to minimize the chance that others will encounter their food in order to prevent future theft.  
Of course we  are not claiming that this is the actual explanation of these findings.  
Our question is not about what scrub-jays actually represent but about what someone could represent that would enable her to track perceptions.
Our claim is that the ability to track perceptions in the ways scrub-jays do could involve representing encounterings only.

@@

For another application of the third principle, consider scrub-jays who strategically re-cache food depending on who saw what.  In one experiment, scrub-jays cached some food in the presence of Competitor A and then cached more food in the presence of Competitor B.  
Later they had an opportunity to recover food in the presence of Competitor A.  
The scrub-jays preferred to recover and re-cache food cached in the presence of Competitor A, leaving untouched food cached in the presence of the absent competitor \citep[][pp.\ 517-9]{en_1418}.  This strategy reduces the chances of Competitor A knowing where any of the scrub-jays’ food is.  What might explain this sensitivity to who saw what in choosing which food to recover?  Clayton and colleagues postulate a capacity to attribute knowledge or `informational states' \citep[]{en_1418}.  They are opposed by Penn and colleagues who postulate that scrub-jays are not ascribing knowledge but using rules such as `Try to re-cache food in a site different from the one where it was cached when the competitor was present' \citep[]{en_1417, Penn:2007ey}.  As an alternative to both proposals, the scrub-jays’ sensitivity could be explained in terms of registration.  Suppose scrub-jays understand that correct registration is a condition on successful goal-directed action.  Then they may be trying to prevent competitors from stealing their cached food by means of preventing them from correctly registering its location.

@@

\section{***BIN***}

With these concepts in place, we can state the second principle: one can’t complete a goal-directed action on an object unless one is encountering it.  So for a goal-directed action to succeed it is not sufficient merely that the object is present; the agent must also be encountering the object.  This principle is not true but it is a useful heuristic.

The hypothesis that an individual tracks what others encounter is sufficient to explain success on some tests for level 1 perspective taking.  \citet[]{en_1550} asked children to hide objects from an experimenter.  The setup meant that the only hiding place left the objects in full view of the child herself.  Even the youngest children tested, two-and-a-half-year-olds, could do this reliably.  They were also able to say who could see an object in different conditions.  The researchers concluded that children can think about seeing:
%
\begin{quote}
`children could conceptually distinguish what they saw from what another person might see, [and] could think about what the other person saw rather than what they saw when asked to do so.'\footnote{
\citet[][p.\ 1210]{en_1550}.
Compare \citet[][p.\ 609]{en_1202} who take subjects' success on a level 1 perspective taking task to show that they
`knew what another person could and could not see when that differed from what they saw'.
}
\end{quote}
%
An alternative hypothesis consistent with these results is that children relied on knowledge of encountering rather than of seeing.  On this hypothesis, children interpreted the experimenter as requesting them to place the object where she would not be encountering it.  And they interpreted questions about who can see what in terms of who is encountering what.
Of course we  are not claiming that this is the best explanation of these findings.  
Our point is just that the ability to track perceptions measured by level 1 perspective taking tasks could involve representing encounterings only and need not involve representing perceptual states as such.

>>>>

%avoid overhang
\tolerance=5000

@@

To make the question more precise it is useful to distinguish 
theory of mind abilities from theory of mind cognition.  
A  \textit{theory of mind ability} 
	\label{df:tom_ability}
is an ability that exists in part because exercising it brings benefits obtaining which depends on exploiting or influencing facts about others’ mental states.
To illustrate,
suppose that Hannah is able to discern whether another's eyes are in view,
that Hannah exercises this ability to escape detection while stealing from others,
that Hannah's ability exists in part because it benefits her in this way,
and 
that Hannah's escaping detection depends on exploiting a fact about other's mental states (namely that they usually cannot  see Hannah's acts of theft when Hannah doesn't have their eyes in view).
Then Hannah has a theory of mind ability.
(This is not supposed to be a plausible, real-world example but only to illustrate what the definition requires.)
An ability to \textit{track} 
	\label{df:track} 
perceptions or beliefs (say) is a theory of mind ability which involves exploiting or influencing facts about these states.
By contrast, \textit{theory of mind cognition} 
	\label{df:tom_cognition}
involves representing mental states or processes as such.
And \textit{full-blown} theory of mind cognition involves  representing propositional attitudes such as beliefs, desires and intentions to construct reason-giving, causal explanations of action.  
The distinction between theory of mind abilities and theory of mind cognition matters because the facts about other minds which theory of mind abilities exploit are not necessarily the facts which are represented in theory of mind cognition.  
To return to the illustration, Hannah is able, within limits, to exploit facts about what others perceive without representing perceptions as such. 
She has a theory of mind ability while possibly lacking any theory of mind cognition.

@@

The notion that some abilities to track perceptions, knowledge states or beliefs involve only theory of mind cognition which does not involve representing perceptions or beliefs as such is not entirely novel.
To mention only those we draw most directly on, Gomez (\citeyear[][p.\ 730]{en_1259}) has emphasized primitive intentional relations to objects established by gaze, O’Neil and Doherty have separately discussed a notion of engagement with objects (\citealp{en_1159, en_1140}), Call and Tomasello (\citeyear[][p.\ 58]{en_1669}) have suggested that chimpanzees track the `likely target' of others’ visual access and understand something about its effects on behaviour, and Whiten (\citeyear[]{en_1415, en_1416}) uses the notion of an `intervening variable' to explain primitive theory of mind notions.  These are illuminating ideas and what follows can be seen as an elaboration and partial synthesis of them.  
The result---minimal theory of mind---is unlike its precursors in that it is rich enough to explain systematic success on a range of false belief tasks.  Our approach is novel in this and others respects to which we return (in the Conclusion) after presenting the substance of our account.

@@

\section{Motivation}
\label{sec:motivation}
Our question is theoretical: it concerns 
not what anyone does represent
but what someone could represent that would enable her, at least within limits, to track perceptions, knowledge states and beliefs.
The motivation for facing up to this question is, of course, partly empirical.

@@

\section{More motivation}
\label{sec:more_motivation} 
Further motivation for our question comes from evidence for theory of mind abilities in young children and infants.
Children in their second year use pointing to provide information to others \citep[]{en_1093} in ways that reflect a partner’s ignorance or knowledge \citep[]{en_1699}, as well as providing more information to ignorant than knowledgeable partners when making requests \citep[]{en_1140}.  One-year-old children also predict actions of agents with false beliefs about the locations of objects \citep[]{en_1092, en_1208} and choose different ways of interacting with others depending on whether their beliefs are true or false \citep[]{en_1783,Knudsen:2011fk,southgate:2010fb}.  And in much the way that irrelevant facts about the contents of others’ beliefs modulate adult subjects’ response times, such facts also affect how long 7-month-old infants look at some stimuli \citep[]{kovacs_social_2010}.

@@

Theory of mind abilities are not only found in humans.
For instance,
scrub-jays can selectively re-cache their food in ways that deprive competitors of knowledge of its location \citep{Clayton:2007fh}, and  chimpanzees can both select routes to approach food which conceal them from a competitor’s view \citep[]{en_1546} and also retrieve food using strategies that optimize their return given what a dominant competitor has seen \citep[]{en_1545}.  
There is debate about the cognitive underpinnings of these abilities. 
Some researchers argue that they may involve representations of nonintentional behaviour only,\footnote{
For example, on chimpanzees: 
	\citet{povinelli:2004vonk}; 
	\citet[pp.\ 364-5]{Vonk:2006cq}; and on scrub-jays and chimpanzees \citet{Penn:2007ey}.
} 
others that they involve representations of perceptions, knowledge states and other propositional attitudes.\footnote{
For example, on chimpanzees: \citet{Tomasello:2005ce,
			Call:2008di}; and on scrub-jays: 
			\citet[p.\ 73]{Emery:2007ze}.
}
If these arguments are not yet decisive
and if the available evidence does not already tightly constrain the space of admissible conjectures,
then the construction of a minimal theory of mind may also be relevant to these debates.
For the conjecture that minimal theory of mind explains chimpanzees' or scrub-jays' abilities to track perceptions or beliefs can be empirically distinguished from conjectures about representations of nonintentional behaviour only and from conjectures about representations of perceptions, knowledge states and beliefs (as we explain in section *** below).

@@

@@

The second principle has many applications.  Someone who is aware of this principle can be motivated to prevent others from encountering her food even when they are not in a position to steal it immediately.  Take scrub-jays.  When choosing where to cache food in the presence of a competitor they prefer far to near, darker to lighter, and occluded to in-view locations \citep[]{en_1451, en_1452}.  These scrub-jays may be trying to hinder future thefts, for these behaviours are not found when caching non-food items \citep[]{en_1419} or when caching in the presence of a partner \citep[][p.\ 514]{Clayton:2007fh, Emery:2007ze}.  Clayton and Emery note that `[s]uch skills suggest visual perspective taking—computing what another can or cannot see' \citep[]{en_1451}. That is to say, they ascribed to scrub jays the concept of seeing.  Another possibility is that scrub-jays compute encountering rather than seeing.  Perhaps scrub-jays take having encountered food to be a condition for performing goal-directed actions targeting that food.  If so they may be trying to minimize the chance that others will encounter their food in order to prevent future theft.  
Of course we  are not claiming that this is the actual explanation of these findings.  
Our question is not about what scrub-jays actually represent but about what someone could represent that would enable her to track perceptions.
Our claim is that the ability to track perceptions in the ways scrub-jays do could involve representing encounterings only.

@@

For another application of the third principle, consider scrub-jays who strategically re-cache food depending on who saw what.  In one experiment, scrub-jays cached some food in the presence of Competitor A and then cached more food in the presence of Competitor B.  
Later they had an opportunity to recover food in the presence of Competitor A.  
The scrub-jays preferred to recover and re-cache food cached in the presence of Competitor A, leaving untouched food cached in the presence of the absent competitor \citep[][pp.\ 517-9]{Clayton:2007fh}.  This strategy reduces the chances of Competitor A knowing where any of the scrub-jays’ food is.  What might explain this sensitivity to who saw what in choosing which food to recover?  Clayton and colleagues postulate a capacity to attribute knowledge or `informational states' \citep[]{Clayton:2007fh}.  They are opposed by Penn and colleagues who postulate that scrub-jays are not ascribing knowledge but using rules such as `Try to re-cache food in a site different from the one where it was cached when the competitor was present' \citep[]{en_1417, Penn:2007ey}.  As an alternative to both proposals, the scrub-jays’ sensitivity could be explained in terms of registration.  Suppose scrub-jays understand that correct registration is a condition on successful goal-directed action.  Then they may be trying to prevent competitors from stealing their cached food by means of preventing them from correctly registering its location.

@@

\subsection{Fourth principle}

So far Lucky thinks of correct registration as a condition for the success of goal-directed action.  This does not tell her anything about what happens if the condition is not met.  In particular it tells her nothing about how an agent will act when she registers an object incorrectly.  The fourth principle involves a switch from thinking of registration as a success condition to thinking of it as a causal factor.  This principle states that when an agent performs a goal-directed action with a goal that specifies a particular object, the agent will act as if the object were in the location she registers it in.

Now that Lucky understands registration as a factor influencing action it can serve her as a proxy for false belief.  Just as, in a limited but useful range of cases, you can track food sources' toxicities by representing their odours
%, objects’ masses by measuring their weights (within limits) 
and prospective sexual partners’ virtues by representing their plumage, so also you can track beliefs by representing registrations.

Applications of the fourth principle therefore include Onishi and Baillargeon’s (\citeyear[]{en_1092}) false belief task.  Subjects are shown an adult observer who is present while a piece of melon is placed in one box.  In the critical condition, the adult observer is then absent while the melon moves to another box.  Comparative looking times indicate that the subjects, who are 14-month-old infants, expect that the adult will reach into the box not containing the melon.\footnote{ 	This finding is supported by a growing body of related research \citep[including][]{en_1666, en_1690, en_1691, en_1208, en_1261}.}  The authors explain this finding by hypothesizing that the infants are ascribing beliefs about the melon’s location to the adults \citep[][p.\ 257]{en_1092}.  Alternatively, the findings could be explained on the hypothesis that they are tracking registration as a cause of action.

\subsection{Extensions and variations}
With the fourth principle we completed the construction of a minimal theory of mind capable of underwriting success on some false belief tasks.  
We stop here because false belief tasks are often taken to be an acid test for theory of mind.
But of course additonal principles can be added accommodate further theory of mind abilities.  
For instance, further principles might extend the definition of registration.  
Registration was been defined as a relation between agents, objects and locations. 
This definition could be extended to include  other types of property as relata in addition to locations.  
Further notions, such as a relational proxy for tracking desires, could also be added.  
These and other modifications would enable hypotheses about minimal theory of mind cognition  to explain a wider range of theory of mind abilities.%
\footnote{
Infants and two-year-olds' theory of mind abilities involve more than tracking false beliefs about location.
To illustrate, \citet{en_1691} show that infants can use communicated information in predicting actions based on false belief, 
\citet{he:2011_false}  show that 2.5-year-olds can succeed on false belief tasks involving unexpected contents rather than location properties, 
and  \citet{en_1795}  show that 18-month olds are sensitive to inferences that others are likely to make. 
}

Variations on the principles are also possible.  To illustrate, scrub-jays’ caching strategies do not obviously call for an ability to track relations to particular food items: their ultimate aim probably isn’t to prevent others pilfering particular worms but to prevent them from pilfering any worms at all.  Accordingly scrub-jays’ protective caching strategies may involve tracking relations between agents, locations and food types rather than particular objects.  
In general it is possible that there is variation across species in what individuals represent that enables them to track perceptions, knowledge states and beliefs. 
If we attempted to characterise theory of mind cognition using only adult human commonsense psychological notions of perception, knowledge and belief, it would be hard to make systematic  sense of the possibility of such variation.
These commonsense psychological notions are not easy to take apart because they resemble the decision-theoretic notion of expected utility in this respect: they are characterised in part by their roles in a system of explanation \citep{Davidson:1985qg,Davidson:1999ju}.
One virtue of the minimal theory of mind construction is that it enables us to make systematic sense of the possibility of variations. 
%Further enhancements will be needed should their general sensitivity to time and episodes also feature in their theory of mind cognition \citep[see][]{en_1409}.

\subsection{But is it theory of mind cognition?}
The term ‘theory of mind’ has been used in several apparently distinct ways \citep[]{en_1415}.  
On some definitions, all theory of mind cognition involves metarepresentation.\footnote{
See \citet{en_81}.  This view can seem obviously correct if it is assumed that  mental states are all representations.
However, there reasons to doubt this assumption \citep[see, for instance, ][]{Campbell:2002ge}.
}  
Minimal theory of mind involves representing goals to which actions are directed, encounterings and registrations, none of which are are representations. 
So if we accepted this definition, what we have constructed would not count as a form of theory of mind cognition just because no metarepresentation is involved.

On another influential definition, theory of mind cognition begins when subjects ascribe states which function as variables intervening between environmental or behavioural inputs and behavioural outputs, and which play some roles characteristic of mental states (\citealp{en_1416}; \citealp[][p.\ 732]{Penn:2007ey}).  
On this definition, the endpoint in our construction (but no earlier point) does count as theory of mind cognition because registrations are intermediate variables and play a subset of the causal roles characteristic of belief.  
For registrations, like beliefs, are characterised by principles generalising across all goal-directed actions,
can be assigned correctness conditions
and causally influence actions.
(Of course they also differ from beliefs in many ways:
they are not propositional attitudes,  they cannot involve reference to never-existent objects and they are not subject to the norms that arguably characterise belief.)
We use the label ‘minimal theory of mind’ because, relative to this definition, the construction describes a minimally elaborate form of theory of mind cognition,
one that does not the entail cognitive and conceptual demands associated with representing perceptions, knowledge states and beliefs as such  
but is capable of grounding theory of mind abilities that generalise across goal-directed actions and are sufficient for systematic success on some false belief tasks.

In what follows we show that minimal theory of mind cognition has clear signature limits.  These limits generate predictions capable of distinguishing hypotheses about minimal theory of mind both 
	from hypotheses  about  representations of nonintentional behaviour only 
	and also 
	from  hypotheses about full-blown theory of mind cognition.

\section{Limits: how to distinguish minimal from full-blown theory of mind cognition}
\label{sec:limits1}
How could we distinguish minimal from full-blown theory of mind cognition experimentally?  The point of minimal theory of mind is to enable agents to fake it—that is, to act as if they were reasoning about propositional attitudes, within limits.  Where a task goes beyond these limits, we can be sure an agent is not using minimal theory of mind only.

Some limits on minimal theory of mind cognition arise from the fact that the theory makes use of objects and their relations to agents, rather than representations of objects, to predict others’ behaviours.  This means that false beliefs involving quantification or identity cannot be tracked by representing registrations.  To see why not, consider the following inference:
%
\begin{quote}
(1) Mitch believes that Charly is in Baltimore.

(2) Charly is Samantha.

Therefore:

(3) Mitch believes that Samantha is in Baltimore.
\end{quote}
%
On almost any account of belief, this inference is not valid
\citep[][pp.\ 214-5]{frege:1948_sense}.  Its central role in a popular film \citep[]{en_1793} indicates that human adults typically appreciate that this inference is not valid.  Contrast the above inference with the corresponding inference in the case of registration:
%
\begin{quote}
(1$'$) Mitch registers \(<\)Charly, Baltimore\(>\)

(2) Charly is Samantha.

Therefore:

(3$'$) Mitch registers \(<\)Samantha, Baltimore\(>\)
\end{quote}
%
This inference from (1$'$) and (2) to (3$'$) is logically valid.  It is valid because registration is a relation to objects.  We can compare registration with other relations like being left of something.  If Charly is Samantha (whether you know it or not), then anyone who is left of Charly is left of Samantha; similarly for registering Charly’s location.

This formal difference between belief and registration entails a limit on minimal theory of mind cognition.  Consider Lucky who tracks beliefs by means of representing registrations only and is unable to represent beliefs. Lucky should have no problem predicting actions based on false beliefs about the locations of objects but she should encounter difficulties in predicting actions based on beliefs essentially involving mistakes about identity.  In particular, Lucky should not be able to understand why, when Mitch registers \(<\)Charly, Baltimore\(>\), he continues searching for Samantha.\footnote{ 	This assumes that Lucky herself knows that Charly is Samantha.  To ease exposition we assume throughout that Lucky has no false beliefs involving identity.}  For to register \(<\)Charly, Baltimore\(>\) is the same thing as registering \(<\)Samantha, Baltimore\(>\). And Lucky should be equally at a loss when those she observes mistakenly believe that two distinct people are identical.  By contrast, subjects who can represent beliefs as such should have no special problem with false beliefs essentially involving identity.  This is how mistakes about the identities of objects can be used to distinguish minimal from full-blown theory of mind cognition.%
\footnote{ 	
Related points about quantification entail further testable distinctions.  For instance, minimal theory of mind should make it impossible to track beliefs whose contents essentially involve \textit{most} objects having a certain property.  It is beyond the scope of this paper to elaborate on these predictions.
}

How could this be exploited experimentally?  One paradigm suitable for infants would involve a puppet which has a concave face and body so that,  unusually, it looks very different when seen from different angles.  Viewed from one angle, the puppet looks like one person (Charly); viewed from another angle, the puppet looks like another person (Samantha); and viewed head-on both aspects of its appearance become visible simultaneously.  Crucially, it is possible to see either aspect without having reason to suppose that the puppet would look so different from another angle.  Subjects sit at a table opposite the protagonist.   There is a screen in the middle of the table which blocks each person’s view of the other side of the table.  In the critical condition, the puppet is initially on the subjects’ side of the screen (see Figure \vref{figure:charlie_samantha_experiment}).  In the first scene, the puppet emerges from the screen so that both observers can see it.  Only one aspect of the puppet is revealed to each; the protagonist sees the Charly-aspect, the subject sees the other aspect.  In the second scene the puppet returns to the subjects’ side of the screen; she then rotates.  The subject but not the protagonist is thereby shown that the face and body have two aspects.  Finally, in scene three, the puppet emerges from the screen.  The puppet again reveals only one aspect of its face and body to each observer but this time the protagonist sees the Samantha-aspect and the subject sees the other aspect.  At this point the puppet leaves the stage altogether. Subjects can see that there is nothing on their side of screen, but the protagonist cannot see this. 
Critically, this means that there is reason for the  protagonist to expect there still to be a puppet (Charly) behind the screen.  
So when, finally, the protagonist reaches around the screen, this action makes sense:
	though there is actually nothing behind the screen, the protagonist has reason to expect there is a puppet.
But for subjects to appreciate that the protagonist has this expectation, and to make sense of her reaching action, they would have to ascribe a false belief about identity.%
\footnote{
	To ensure this, the design must be such that subjects cannot readily categorise the puppet’s two appearances and such that subjects do not use verbal labels for the two aspects.  Otherwise it would be possible for subjects to infer the protagonist’s expectation by reasoning about types of object. 
}  
Subjects' lack of surprise at the protagonist's reaching around the screen (as compared to  a control condition which differs from this one only in that the protagonist manifestly knows that the two aspects of the puppet’s face and body are aspects of a single puppet) would therefore be evidence that they can track false beliefs about identity.  
This would be evidence for full-blown, not minimal, theory of mind.

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{figure_charlie_samantha_experiment.png}
\caption{
\label{figure:charlie_samantha_experiment}
	How to test whether infants can ascribe false beliefs about identity.  The subject is in the foreground with only the back of  her head visible; the protagonist sits opposite, facing the subject.  A screen conceals some of the action from the protagonist.
}
\end{center}
\end{figure}

So far we have discussed mistaken beliefs about identity where the truth of the belief would require there to be more individuals in the world (Charly and Samantha; a teacher and an assassin) than there actually are.  The converse is also possible \citep[see, e.g.,][]{en_1794}.  Here the mistake is to have beliefs whose truth would require there to be fewer individuals in the world than there actually are. The main condition of a possible experiment is outlined in Figure \vref{figure:identity_balls_experiment}.  In this experiment there are two perceptually indistinguishable balls.  Whereas subjects can see both balls simultaneously, a screen ensures that the protagonist never sees both at once.  The movements of the two balls are timed in such a way that what the protagonist sees indicates the existence of a single ball.%
\footnote{ 	
Song and Baillargeon (\citeyear[]{en_1823}) provide evidence that 15-month-old infants are able to predict actions on the basis of how things appear to observers who are ignorant of their true nature. \citet{en_1822} show that chimpanzees also make inferences about the appearances of things in predicting behaviours. These and other findings \citep[e.g.][]{en_1820} suggest that infants and perhaps others are generally sensitive to facts about the ways things look in tracking others’ beliefs. 
}
When the protagonist sees a ball appear from behind the screen and leave the scene (panels 5-7 in Figure 5), this provides a reason for the protagonist to believe that there is nothing behind the screen.  Infants could only be sensitive to this belief if they were able to track beliefs involving identity.  Sensitivity to this belief might be manifested by comparing this condition with a modified condition in which the protagonist  manifestly knows that there are two balls.  If subjects show more surprise when the protagonist reaches around the screen (say) in the original condition than in the modified condition, this too would be evidence for full-blown over minimal theory of mind cognition.

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{figure_identity_balls_experiment.png}
\caption{
\label{figure:identity_balls_experiment}
	How to test whether infants can ascribe false beliefs about identity where the mistake involves belief whose truth would entail that there were fewer objects than there in fact are.  As in Figure \ref{figure:charlie_samantha_experiment}, the subject is in the foreground with only the back of  her head visible; the protagonist sits opposite, facing the subject.  A screen conceals some of the action from the protagonist.
}
\end{center}
\end{figure}

Given that this analysis, it is notable that one study already claims to have found positive evidence that infants can ascribe beliefs about identity. 
Scott and Baillargeon (\citeyear{en_1690}) have already conducted experiments which aim to show that 18-month-old infants are able to represent beliefs involving mistakes about `which particular object \textit{token}' another is facing rather than only about `which \textit{type} of object' is present (p.\ 1179). However, while their aim is clearly relevant, we shall show that these experiments do not succeed in testing whether infants ascribe beliefs about identity.  In essence, their paradigm involves two types of object, a divisible penguin which affords hiding a key and an indivisible penguin which lacks this affordance.  The divisible penguin has two states, divided and whole.  When whole it is visually indistinguishable from the indivisible penguin which does not afford hiding a key.  Infants sit opposite a protagonist.  Familiarisation trials provide information that the protagonist can expect there to be two penguins in the scene at all times, one of each type; these trials also provide information that the protagonist can expect the divisible penguin to appear in its divided state. In the critical condition, the scene contains an uncovered and a covered penguin. The uncovered penguin is divisible but, because it is in the whole state, it might easily be taken to be indivisible.  The covered penguin is indivisible.  The findings suggest that infants know that the uncovered penguin is divisible but expect the protagonist to believe that the uncovered penguin is indivisible and to infer that the covered penguin is divisible.  Does this pattern of knowledge and expectation require that the infants have attributed a false belief about identity?  This is not necessary. Suppose that infants attributed the following reasoning to the protagonist: this penguin visible on my right is \textit{an} indivisible penguin; \textit{a} divisible penguin is always present; therefore there is \textit{a} divisible penguin under the cover.  This reasoning concerns only the types of objects present and does not involve identity. Yet it is sufficient (together with some further inferences about the protagonists’ goal) for success. So while Scott and Baillargeon’s (2010) findings are interesting in many respects, their implementation does not provide evidence that infants ascribe beliefs about identity.

In this section we have explained ways of distinguishing minimal theory of mind cognition from its full-blown counterpart.  Where subjects are able to track beliefs about identity we know they are not relying only on minimal theory of mind; and, conversely, where subjects are able to track beliefs about objects’ properties but not about identity, we can infer that they are not using full-blown theory of mind.  We next consider how  minimal theory of mind might be distinguished experimentally from strategies which involve representing nonintentional behaviour only.

\section{Limits: how to distinguishing minimal theory of mind from behavioural strategies}
\label{sec:limits2}
What could show that subjects are not solving a task by representing nonintentional behaviour only but are using minimal theory of mind or something stronger?  
We shall use the term ‘behavioural strategy’ to refer to processes underpinning theory of mind abilities which involve representing nonintentional behaviours only.

An obstacle to distinguishing minimal theory of mind from behavioural strategies is that there is no in-principle limit to the complexity of the predictions which behavioural strategies might support.  The behaviour-representing counterpart of Laplace’s demon knows our entire behavioural histories, has perfect knowledge of the regularities governing object-directed actions and is not limited by scarce cognitive resources.  This demon can readily predict our future behaviours without any theory of mind.

One way to avoid the problem of the behaviour-representing demon is to set tasks involving explanation rather than prediction \citep[compare][p.\ Chapter 8]{en_167}.  Subjects observe a standard false belief scenario in which a character, Maxi, first searches for an object in the wrong location.  The test question is why Maxi searched as he did \citep[see e.g.][]{en_80, en_352}.  Where subjects’ answers include reference to incorrect registration or a related notion (which might, of course, be verbalised in terms of what an agent ‘thinks’), they have at least minimal theory of mind cognition.  Of course, this only works where subjects can be asked ‘why’ questions.

For other subjects we need an indirect measure.  If subjects sometimes represent encounters or perceptions as such, then representations of others’ encounters may interfere with expectations or judgements about reality or with judgements about one’s own perceptions and beliefs \citep[so-called `altercentric interference',][]{Samson:2010jm}.  For example, representing a protagonists’ encounter with an object at a particular location may interfere with expectations about the object’s actual location.  Accordingly, evidence that there is such interference when in a situation where others have different perceptions or beliefs would provide indirect evidence for theory of mind cognition (minimal or full-blown) over behavioural strategies, for such interference would be difficult to explain if subjects were representing behaviours only. Evidence showing this kind of altercentric interference has recently been found in human adults \citep[]{en_1797, Samson:2010jm}. These studies show that adults’ judgements about the number of objects they could see in a visual scene were slower and more error-prone when the scene contained an irrelevant other whose perspective was different, suggesting that another’s perspective can cause altercentric interfere.

Of course it was never in question that adults represent encounters or perceptions and not only behaviours; the relevance of these studies is that they demonstrate that altercentric interference can be used as an indirect measure for distinguishing behavioural strategies from minimal theory of mind cognition.  \citet[]{kovacs_social_2010} report evidence of altercentric interference in infants’ expectations about the presence of an object.  Their study suggests that infants’ surprise when their expectations about an object’s presence or absence are violated is modulated by facts about another’s expectations about that object’s location.  Infants looked for less time at the unexpected presence of an object behind a screen when another observer incorrectly expected it to be there than when the observed did not expect it to be there. These findings seem to be evidence of altercentric interference, which is consistent with either minimal or full-blown theory of mind but difficult to explain if participants are exclusively using behavioural strategies.

A related way to distinguish behavioural strategies from minimal theory of mind or something stronger is by means of self-other inference.  Emery and Clayton (\citeyear[]{en_1411}) divided scrub-jays into those who had previously pilfered food and those who had never pilfered.  All subjects then cached some food in private and cached some more food while being observed.  When later given privacy, the pilferers re-cached the food they had earlier cached in the presence of the observer but did not re-cache the food they had cached in private.  The non-pilferers did not show this pattern of behaviour and did little re-caching.\footnote{ 	Similar results might be found if this paradigm were adapted for human infants \citep[see][]{en_1707}.}  This is difficult to reconcile with the hypothesis that scrub-jays rely entirely on behavioural strategies.  By contrast, the hypothesis that scrub-jays have at least minimal theory of mind and so are able to represent goal-directed actions as such allows us to suppose that engaging in pilfering alerts them to the possibility that others may do the same.\footnote{ 	In later discussions these authors claim that the pilferers may be projecting their own experiences onto others in the sense that they are using `their own experiences to infer experiences in others' \citep[][p.\ 81]{Emery:2007ze}.  This claim goes beyond our suggestion, which involves goals rather than experiences and salience rather than projection.  }

Another route to distinguishing minimal theory of mind cognition from behavioural strategies derives from an analogy with speech perception.  It is well established that phoneme recognition is facilitated by lexical information \citep[]{en_1704}.  Similarly, for subjects with (at least) minimal theory of mind cognition, there is evidence that identification of significant segments of behaviour is facilitated by information about goals.  For instance, Zacks (\citeyear[]{en_1442}) varied the availability of information about goals while holding motion features of behaviour constant.  He found that subjects given information about goals segmented behaviour differently from subjects not given such information.  Of course for Zacks it was not in question that his subjects could represent goals; the issue was how their representation of goals interacted with their representations of behaviour.  But with modification the  paradigm could be used to test participants who are not already known to be capable of representing goals.  If making information about goals, encounterings or registrations available alters how subjects segment behaviours, this would be evidence that they are not relying on behavioural strategies only.
